---
title: "Akshara R_Assignment Review by Lakpa"
output: html_document
date: "2025-03-25"
---


```{r}
library(tidyverse)
library(tidyr)
```
#Comment: Your data inspection part is missing. Please complete it as part I section. 
# At the start of your analysis

```{r}
str(transposed_group)
summary(snp_position)
file.info("fang_et_al_genotypes.txt") 
file.info(:snp_position.txt")
```

#Comment: You haven't created maize file so I cannot find this object to run following code. This appeards to be missing step. 

#Comment: You are reading same files mutliple times unnecessarily. 
# Read files once at the beginning. 

```{r}
transposed_group <- read.delim("transposed_genotypes.txt", stringsAsFactors = FALSE)
snp_position <- read.delim("snp_position.txt", stringsAsFactors = FALSE)
```

#Remove any empty {r} blocks
```{r}
colnames(transposed_group_new)<- as.character(transposed_group_new[1,])
transposed_group_new[-c(1),]
#merging the columns
merge<- merge(snp_position,transposed_group_new, by.x = "SNP_ID", by.y = "Group", all=TRUE)

```

```{r}
```

#you haven't change the ?/? into -/- for decreasing order for both teosinte and maize. I have provided an example for the code. 
# Replace "?/?" with "-/-"
```{r}
teosinte_chr_decreasing[teosinte_chr_decreasing == "?/?"] <- "-/-"

```
#Comment: Good use of ggplots for visualization.SNP distribution plot could compare maize/Teosinte
```{r}
# Current only shows overall distribution
# Could add:
merged_data %>%
  mutate(Group = ifelse(grepl("^ZMM", names(.)), "Maize", "Teosinte")) %>%
  group_by(Chromosome, Group) %>%
  tally() %>%
  ggplot(aes(x=Chromosome, y=n, fill=Group)) + 
  geom_col(position="dodge")
```
#Comment: Missing data visualizaation missing. You can create a bar plot of missing genotype proportions across different groups.Overall, nice job. 

